\documentclass{llcns}
\usepackage[hyphens]{url}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{multirow, enumitem, subfigure}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage[normalem]{ulem}
\usepackage{caption}
\usepackage{color}
\usepackage{soul, textcomp}


\title{P4: Peer Feedback and Response}

\author{Utkarsh Goel \and Clint Cooper}
\institute{Department of Computer Science\\Montana State University, Bozeman MT 59717\\
\email{\{utkarsh.goel, clint.cooper\}@montana.edu}
}


\date{March 2016}

\begin{document}
\maketitle

\section{Peer Feedback}

\subsection{Summary}
According to the feedback from our peers, we gathered several primary points that we have ordered below: 
\begin{itemize}
    \item Motivation was well explained.
    \item We provided detailed and an easy-to-understand background on the problem.
    \item Our peers well understood the real world application of our project -- why the project is going to be useful, for whom it will be useful.
    \item People were also satisfied with the figures we used in our slides. Instead, the choice of our figures helped many to understand the problem statement more clearly.
    \item We invested more time explaining the proposed problem and how exactly the problem was significant in the real world scenarios, as opposed to spending more time on reflecting on significant details of our solution.
\end{itemize}

\subsection{Our Response}

First of all, we thank all of our peers who provided us feedback.
We consider this feedback as valuable and helpful towards refining our project details for future presentations.
Each of the following sections addresses one or more comments that we received from our peer reviews.

\subsubsection*{Great motivation, detailed explanation, good use of figures, useful real-world apps\\}

With respect to feedback on technical content during our presentation, we are excited to learn that we were able to motivate the people in the audience about the problem we are working on.
Given that we only received positive feedback from our peers about the motivation, we conclude that our approach to organize the slides and story was helpful to the audience.
We plan to continue to use similar structure for future presentations.

\subsubsection*{Not much time spent on solution\\}

With respect to feedback on our proposed solution, we argue that our goal for this presentation was to motivate our peers about the problem, instead of how exactly we are solving the problem. 
Further, since we assume that this presentation was preliminary because it was scheduled in middle of the semester, and also because we had restricted time for presentation, we planned to offer only a limited discussion on our upcoming solutions. 
We mention this due to a few of the peer reviews commenting that we were not as technical in our presentation as expected.

\section{Self Evaluation}

\subsection{Member Contributions}

The team members worked almost exclusively together on all parts of this project. We plan to continue this team work for the remainder of the semester to further evolve this project. We believe this style of collaboration will yield the best results in the most timely manner. 

\subsection{Biggest Challenge}

Our group has not yet encountered any real challenges thanks to bi-weekly meetings with professors. As of now, we have had ample time to address each challenge before we faced them. Any difficulties we have encountered, we had planned for and became non-issues almost immediately. 

\subsection{Presentation Questions}

\begin{enumerate}
    \item How do the proxies work?
    \item How did we get our DNS data?
\end{enumerate}

\subsection{Addressing Peer Feedback}

\begin{enumerate}
    \item Proxies split the end-to-end communications of the clients and origin servers. The data meant to travel to the origin server is instead transmitted to the proxies which in turn transmits it to the origin server and awaits the response. Upon receiving the response from the origin server, the proxy will retransmit to the client.
    \item The DNS data was provided by Information Technology Center (ITC) at Montana State University (MSU). This data was collected over the course of 24 hours and composed of anonymous traffic generated by users of the Internet while on campus. 
\end{enumerate}


\end{document}
