\documentclass{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}

\title{P7: Peer Feedback and Response}
\author{Utkarsh Goel and Clint Cooper\\ \large \textit{(Group 5)}}
\date{}

\begin{document}
\maketitle

\section{Peer Feedback Summary}
According to the feedback from our peers, we classify feedback into several primary points: 
\begin{itemize}
    \item The motivation of our project was very well explained. 
    Our presentation allowed people to completely follow the content we discussed.
    \item We provided detailed and an easy-to-understand background on the problem.
    One of the reasons for this, as mentioned in the feedback, is that we had a well-defined story to tell and we were not too fast when discussing technical details.
    \item Our peers understood the real world applications of our project -- why the project is going to be useful and for whom it will be useful.
    \item People were also satisfied with the figures we used in our slides. In fact, the choice of our figures helped many to understand the problem statement more clearly.
    \item Finally, we did not receive any negative comment about neither the technical content and nor for our presentation.
    However, we did receive some interesting questions that we might want to look into as an extension to this work.
\end{itemize}

\section{Our Response to Feedback}

First of all, we thank all of our peers who provided us with detailed feedback.
We consider this feedback very valuable and helpful towards refining our presentations for future projects.
Each of the following subsections address one or more comments that we received from our peers.

\subsubsection*{Great motivation, detailed explanation, good use of figures, useful real-world applications}

With respect to feedback on technical content during our presentation, we are excited to learn that we were able to motivate the people in the audience about the problem we are working on.
Given that we only received positive feedback from our peers about the motivation, we conclude that our approach to organize the slides and story was helpful to the audience.
We plan to continue to use a similar structure for future presentations.

\subsubsection*{Interesting Questions Asked}

One of the interesting questions asked was how one could personalize webpage pre-fetching based on individual users.
We have considered this and we have plans to look into this as a course project for the data mining course that we both are planning to take next semester.
One of the things one could do, is install a plugin on the user's home router. 
The plugin would send DNS or HTTP data to our servers where it would be processed.
Since the data transmitted would be based on individual users, one could predict what individual users interests are.

\end{document}
